The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2012-12-17 script/de/chapters/primes.tex
CT script: Minor formal changes in chapter 3

Sein Beweis, dass es unendlich viele Primzahlen gibt, gilt bis heute als 
ein Glanzstück mathematischer Überlegung und Schlussfolgerung 
(\textbf{Widerspruchsbeweis}\index{Widerspruchsbeweis}). 
Er nahm an, es gebe nur endlich viele Primzahlen und damit eine größte
Primzahl. Daraus zog er solange logische Schlüsse, bis er auf einen
offensichtlichen Widerspruch stieß. Damit musste etwas falsch sein. Da 
sich in die Schlusskette kein Lapsus eingeschlichen hatte, konnte es nur 
die Annahme sein. Demnach musste es unendlich viele Primzahlen geben!

\hypertarget{euklid}{}
\paragraph*{Euklids Widerspruchsbeweis}
% Bei /paragraph den * angefügt, damit es auch bei 4 Ebenen nicht in Inh.verzecihnis
\index{Euklids Widerspruchsbeweis}\index{Widerspruchsbeweis}
führt die Argumentation wie folgt:

\begin{Beweis}{}
{\bf Annahme:} \quad Es gibt {\em endlich} viele Primzahlen.
\\*[4pt] {\bf Schluss:} \quad Dann lassen sie sich auflisten $p_1
< p_2 < p_3 < \dots < p_n$, wobei $n$ für die (endliche) Anzahl
der Primzahlen steht. $p_n$ wäre also die größte Primzahl. Nun
betrachtet Euklid die Zahl $a = p_1 \cdot p_2 \cdots p_n +1$.
Diese Zahl kann keine Primzahl sein, da sie in unserer
Primzahlenliste nicht auftaucht. Also muss sie durch eine Primzahl
teilbar sein. D.h. es gibt eine natürliche Zahl $i$ zwischen $1$
und $n$, so dass $p_i$ die Zahl $a$ teilt. Natürlich teilt $p_i$
auch das Produkt $a-1 = p_1 \cdot p_2 \cdots p_n$, da $p_i$ ja ein
Faktor von $a-1$ ist. Da $ p_i $ die Zahlen $ a $ und $ a-1 $
teilt, teilt sie auch die Differenz dieser Zahlen. Daraus folgt:
$p_i$ teilt  $a - (a-1) = 1$. $p_i$ müsste also $1$ teilen und
das ist unmöglich.\\*[4pt] 
{\bf Widerspruch}: \quad Unsere Annahme war falsch.\par
Also gibt es {\em unendlich} viele Primzahlen
(siehe \hyperlink{primhfk}{Übersicht unter \ref{s:primhfk}} über die
Anzahl von Primzahlen in verschiedenen Intervallen).
\end{Beweis}

@@

Mersenne behauptete, dass $2^{67}-1$ eine Primzahl ist. Auch zu
dieser Behauptung gibt es eine interessante mathematische Historie:
Zuerst dauerte es über 200 Jahre, bis \index{Lucas, Edouard}
Edouard Lucas (1842-1891) bewies, dass diese Zahl zusammengesetzt
ist. Er argumentierte aber indirekt und kannte keinen der
Faktoren. 1903 zeigte Frank Nelson Cole\index{Cole, Frank Nelson}\footnote{%
Frank Nelson Cole, amerikanischer Mathematiker, 20.09.1861$-$26.05.1926.},
aus welchen Faktoren diese Primzahl besteht:
$$ 2^{67} -1 =147. 573. 952. 589. 676. 412. 927 = 193. 707. 721 \cdot 761. 838. 257. 287. $$
Er gestand, 20 Jahre an der Faktorisierung \index{Faktorisierung} (Zerlegung in Faktoren)%
\footnote{%
  Mit CT1\index{CrypTool 1} können Sie Zahlen auf folgende Weise 
  faktorisieren: Menü {\bf Einzelverfahren \textbackslash{} RSA-Kryptosystem 
  \textbackslash{} Faktorisieren einer Zahl}. \\
  In sinnvoller Zeit zerlegt CT1 mit dem Quadratischen Sieb (QS) auf einem Einzel-PC
  Zahlen bis 250 Bit Länge.
  Zahlen größer als 1024 Bit werden zur Zeit von CT1 nicht angenommen.\\
  Mit CT2 kann man sowohl das QS als auch das GNFS (General Number Field Sieve)
  anwenden und die Berechnungen auf mehrere Rechner verteilen.\\
  Die aktuellen Faktorisierungsrekorde finden Sie in Kapitel
  \ref{nt:NoteFactorization}.
  \index{Faktorisierung!Faktorisierungsrekorde}
}
dieser 21-stelligen Dezimalzahl gearbeitet zu haben!

@@

Ähnlich einfach kann man zeigen, dass aus der schwachen Golfbach-Vermutung die oben
erwähnte Behauptung von Terence Tao folgt (beide gelten für ungerade Zahlen):\\
- Für ungerade Zahlen $u>5$ folgt direkt aus der schwachen Goldbach-Vermutung, dass die Summe aus höchstens fünf Primzahlen besteht.\\
- Für die restlichen ungeraden Zahlen $3$ und $5$ kann man es direkt einsetzen: $3 = 3$ (die \glqq Summe\grqq~ hat nur einen und damit höchstens fünf prime Summanden); $5 = 2 + 3$ (die Summe hat zwei und damit höchstens fünf prime Summanden).

@@

\item Ausgabe der $n$-ten Primzahl \\
      \url{http://www.utm.edu/research/primes/notes/by_year.html}

>>>>

Sein Beweis, dass es unendlich viele Primzahlen gibt, gilt bis heute als 
ein Glanzstück mathematischer Überlegung und Schlussfolgerung 
(\textbf{Widerspruchsbeweis}\index{Widerspruchsbeweis}). 
Er nahm an, es gebe nur endlich viele Primzahlen und damit eine größte
Primzahl. Daraus zog er solange logische Schlüsse, bis er auf einen
offensichtlichen Widerspruch stieß. Damit musste etwas falsch sein. Da 
sich in die Schlusskette kein Lapsus eingeschlichen hatte, konnte es nur 
die Annahme sein. Demnach musste es unendlich viele Primzahlen geben!\\

\hypertarget{euklid}{}
\index{Euklids Widerspruchsbeweis}\index{Widerspruchsbeweis}
% \paragraph*{Euklids Widerspruchsbeweis}
% Bei /paragraph den * angefügt, damit es auch bei 4 Ebenen nicht im Inh.verzeichnis erscheint
% führt die Argumentation wie folgt:
\begin{Beweis}{nach Euklid (Widerspruchsbeweis)\\}
{\bf Annahme:} \quad Es gibt {\em endlich} viele Primzahlen.
\\*[4pt] {\bf Schluss:} \quad Dann lassen sie sich auflisten $p_1
< p_2 < p_3 < \dots < p_n$, wobei $n$ für die (endliche) Anzahl
der Primzahlen steht. $p_n$ wäre also die größte Primzahl. Nun
betrachtet Euklid die Zahl $a = p_1 \cdot p_2 \cdots p_n +1$.
Diese Zahl kann keine Primzahl sein, da sie in unserer
Primzahlenliste nicht auftaucht. Also muss sie durch eine Primzahl
teilbar sein. D.h. es gibt eine natürliche Zahl $i$ zwischen $1$
und $n$, so dass $p_i$ die Zahl $a$ teilt. Natürlich teilt $p_i$
auch das Produkt $a-1 = p_1 \cdot p_2 \cdots p_n$, da $p_i$ ja ein
Faktor von $a-1$ ist. Da $ p_i $ die Zahlen $ a $ und $ a-1 $
teilt, teilt sie auch die Differenz dieser Zahlen. Daraus folgt:
$p_i$ teilt  $a - (a-1) = 1$. $p_i$ müsste also $1$ teilen und
das ist unmöglich.\\*[4pt] 
{\bf Widerspruch}: \quad Unsere Annahme war falsch.\par
Also gibt es {\em unendlich} viele Primzahlen
(siehe \hyperlink{primhfk}{Übersicht unter \ref{s:primhfk}} über die
Anzahl von Primzahlen in verschiedenen Intervallen).
\end{Beweis}

@@

Mersenne behauptete, dass $2^{67}-1$ eine Primzahl ist. Auch zu
dieser Behauptung gibt es eine interessante mathematische Historie:
Zuerst dauerte es über 200 Jahre, bis \index{Lucas, Edouard}
Edouard Lucas (1842-1891) bewies, dass diese Zahl zusammengesetzt
ist. Er argumentierte aber indirekt und kannte keinen der
Faktoren. 1903 zeigte Cole\index{Cole, Frank Nelson}\footnote{%
Frank Nelson Cole, amerikanischer Mathematiker, 20.09.1861$-$26.05.1926.},
aus welchen Faktoren diese Primzahl besteht:
$$ 2^{67} -1 =147. 573. 952. 589. 676. 412. 927 = 193. 707. 721 \cdot 761. 838. 257. 287. $$
Er gestand, 20 Jahre an der Faktorisierung \index{Faktorisierung} (Zerlegung in Faktoren)%
\footnote{%
  Mit CT1\index{CrypTool 1} können Sie Zahlen auf folgende Weise 
  faktorisieren: Menü {\bf Einzelverfahren \textbackslash{} RSA-Kryptosystem 
  \textbackslash{} Faktorisieren einer Zahl}. \\
  In sinnvoller Zeit zerlegt CT1 mit dem Quadratischen Sieb (QS) auf einem Einzel-PC
  Zahlen bis 250 Bit Länge.
  Zahlen größer als 1024 Bit werden zur Zeit von CT1 nicht angenommen.\\
  Mit CT2 kann man sowohl das QS als auch das GNFS (General Number Field Sieve)
  anwenden und die Berechnungen auf mehrere Rechner verteilen.\\
  Die aktuellen Faktorisierungsrekorde finden Sie in Kapitel
  \ref{nt:NoteFactorization}.
  \index{Faktorisierung!Faktorisierungsrekorde}
}
dieser 21-stelligen Dezimalzahl gearbeitet zu haben!

@@

Ähnlich einfach kann man zeigen, dass aus der schwachen Golfbach-Vermutung die
oben erwähnte Behauptung von Terence Tao folgt (beide gelten für ungerade
Zahlen):
\begin{itemize}	
   \item Für ungerade Zahlen $u>5$ folgt direkt aus der schwachen
      Goldbach-Vermutung, dass die Summe aus höchstens fünf Primzahlen besteht.
   \item Für die restlichen ungeraden Zahlen $3$ und $5$ kann man es direkt
      einsetzen:\\
      $3 = 3$ (die \glqq Summe\grqq~hat nur einen und damit höchstens
      fünf prime Summanden);\\
      $5 = 2 + 3$ (die Summe hat zwei und damit höchstens fünf prime Summanden).
\end{itemize}

@@

\item Ausgabe der $n$-ten Primzahl P(n)\\
      \url{http://www.utm.edu/research/primes/notes/by_year.html}

### 2012-12-17 script/en/chapters/primes.tex
CT script: Minor formal changes in chapter 3

Although there are only $92$ natural chemical elements, the number of prime
numbers is unlimited. Even the Greek, \index{Euclid} Euclid%
\footnote{Euclid,
a Greek mathematician of 4th and 3rd century B.C. He worked at the
Egyptian academy of Alexandria and wrote ``The Elements'', the most well 
known systematically textbook of the Greek mathematics.} 
knew this in the third century B.C.
\begin{theorem}[Euclid\footnote{The common usage of the term does not denote Euclid as the inventor of the theorem rather;
the true inventor is merely not as prominent. The theorem has already been distinguished
and proven in Euclid's Elements (Book IX, theorem 20). The phraseology is remarkable due to 
the fact that the word infinite is not used. The text reads as followed
$$
O\acute{\iota}~\pi\varrho\tilde{\omega}\tau o \iota~\grave{\alpha}\varrho\iota\vartheta\mu o\grave{\iota}~
\pi\lambda\varepsilon\acute{\iota}o \upsilon\varsigma~\varepsilon\grave{\iota}\sigma\grave{\iota}~
\pi\alpha\nu\tau\grave{o}\varsigma~\tau o \tilde{\upsilon}~
\pi\varrho o \tau\varepsilon\vartheta\acute{\varepsilon}\nu\tau o \varsigma~
\pi\lambda\acute{\eta}\vartheta\ o \upsilon\varsigma~
\pi\varrho\acute{\omega}\tau\omega\nu~
\grave{\alpha}\varrho\iota\vartheta\mu\tilde{\omega}\nu,
$$
the English translation of which is: the prime numbers are more than 
any previously existing amount of prime numbers.
}]\label{thm-pz-euklid} % Ende der Fuﬂnote
% Fussnote VOR "]" in [Euclid], damit kein Leerraum vor der Fussnotennummer.
% Vorher stand da: ...(Euclid). BLANK Fussnote und das Blank stoerte.
% Nun steht die Fussnote direkt hinter "Euclid" und vor der ")".
% Eigentlich h‰tte ich sie gerne direkt hinter "(Euclid)", noch vor dem 
% automatisch gesetzten Punkt. 
The sequence of prime numbers does not discontinue.
Therefore, the quantity of prime numbers is infinite.
\end{theorem}
His proof that there is an infinite number of
primes is still considered to be a brilliant mathematical consideration and
conclusion today (\textbf{proof by contradiction} \index{Proof by contradiction}). 
He assumed that there is only a finite number of primes and therefore a 
largest prime number. Based on this assumption, he drew logical conclusions
until he obtained an obvious contradiction. This meant that something must
be wrong. As there were no mistakes in the chain of conclusions, it could
only be the assumption that was wrong. Therefore, there must be an infinite
number of primes!

\hypertarget{euclid}{}
\paragraph*{Euclid's proof by contradiction}
\index{Euclid's proof by contradiction}\index{Proof by contradiction}
goes as follows:

\begin{Proof}{}
{\bf Assumption:} \quad There is a {\em finite} number of primes. \\*[4pt] {\bf
Conclusion:} \quad Then these can be listed $p_1 < p_2 < p_3 < \dots < p_n$,
where $n$ is the (finite) number of prime numbers. $p_n$ is therefore the
largest prime. Euclid now looks at the number $a = p_1 \cdot p_2 \cdots p_n +1$.
This number cannot be a prime number because it is not included in our list of
primes. It must therefore be divisible by a prime, i.e. there is a natural
number $i$ between $1$ and $n$, such that $p_i$ divides the number $a$. Of
course, $p_i$ also divides the product $a-1 = p_1 \cdot p_2 \cdots p_n$, because
$p_i$ is a factor of $a-1$. Since $ p_i $ divides the numbers $ a $ and $ a-1 $,
it also divides the difference of these numbers. Thus: $p_i$ divides  $a - (a-1)
= 1$. $p_i$ must therefore divide $1$, which is impossible. \\*[4pt] {\bf
Contradiction:} \quad Our assumption was false.

@@

Mersenne claimed that $2^{67}-1$ is a prime number. There is also a mathematical
history behind this claim: it first took over 200 years before 
\index{Lucas, Edouard} Edouard Lucas (1842-1891) proved that this number 
is composite.
However, he argued indirectly and did not name any of the factors. In 1903,
Frank Nelson Cole\index{Cole, Frank Nelson}\footnote{%
Frank Nelson Cole, American mathematician, Sep. 20, 1861 $-$ May 26, 1926.}
showed which factors make up this composite number: 
$$ 2^{67} -1
=147, 573, 952, 589, 676, 412, 927 = 193, 707, 721 \cdot 761, 838, 257, 287. $$
He admitted to having worked 20 years on the factorization 
\index{Factorization} (expression as a product of prime factors)\footnote{%
  Using CT1\index{CrypTool 1} you can factorize numbers in the 
  following way: menu {\bf Indiv. Procedures \textbackslash{} RSA Cryptosystem 
  \textbackslash{} Factorization of a Number}. \\
  CT1 can factorize with the quadratic sieve (QS) on a single PC in a reasonable
  time numbers no longer than 250 bit.
  Numbers bigger than 1024 bits are currently not accepted by CT1. \\
  With CT2 you can use both the QS and the GNFS (general number field sieve),
  and CT2 can distribute the calculations on several computers.\\
  The current factorization records are listed in chapter \ref{nt:NoteFactorization}.
  \index{Factorization!factoring records}
}
of this 21-digit decimal number!

@@

% --------------------------------------------------------------------------
% \vskip +10 pt
\newpage
\subsection{Unproven statements / conjectures about primes / Further open questions}
\begin{itemize}
  \item Goldbach\footnote{%
     Christian Goldbach\index{Goldbach, Christian}, German mathematician,
     Mar 18, 1690$-$Nov 20, 1764. }
     conjectured: Every even natural number greater than 2 can
     be represented as the sum of two prime numbers.

@@

% --------------------------------------------------------------------------
\vskip +10 pt
\hypertarget{HT-GoldbachConjecture}{}
\subsection{The Goldbach Conjecture}
\label{L-GoldbachConjecture}

@@

Similarily easy it can be shown, that the weak Goldbach conjecture implies the above mentioned conjecture from Terence Tao (both hold for odd numbers):\\
- For odd numbers $u>5$ directly the weak Goldbach conjecture implies that the sum consits at most of five primes.\\
- For the remaining odd numbers $3$ and $5$ you can directly check it: $3 = 3$ (the ``sum'' has only one and therefore at most five prime summands); $5 = 2 + 3$ (the sum has two  and therefore at most five prime summands).

@@

For larger sequences, it is impractical to print all single messages indicating the
primality of integers. In the following Sage session, only the statitics at the end
is printed (by setting the verbose parameter to false): the overall number of primes
and the percentage of primes, generated by $f(n)$ where $0 \leq n \leq 1000$.

@@

% --------------------------------------------------------------------------
\newpage
\section*{Web links} \addcontentsline{toc}{section}{Web links}

@@

\item Showing the $n$-th prime number \\
      \url{http://www.utm.edu/research/primes/notes/by_year.html}

>>>>

Although there are only $92$ natural chemical elements, the number of prime
numbers is unlimited. Even the Greek, \index{Euclid} Euclid%
\footnote{Euclid,
a Greek mathematician of 4th and 3rd century B.C. He worked at the
Egyptian academy of Alexandria and wrote ``The Elements'', the most well 
known systematically textbook of the Greek mathematics.} 
knew this in the third century B.C.
\begin{theorem}[Euclid\footnote{The common usage of the term does not denote Euclid as the inventor of the theorem rather;
the true inventor is merely not as prominent. The theorem has already been distinguished
and proven in Euclid's Elements (Book IX, theorem 20). The phraseology is remarkable due to 
the fact that the word infinite is not used. The text reads as followed
$$
O\acute{\iota}~\pi\varrho\tilde{\omega}\tau o \iota~\grave{\alpha}\varrho\iota\vartheta\mu o\grave{\iota}~
\pi\lambda\varepsilon\acute{\iota}o \upsilon\varsigma~\varepsilon\grave{\iota}\sigma\grave{\iota}~
\pi\alpha\nu\tau\grave{o}\varsigma~\tau o \tilde{\upsilon}~
\pi\varrho o \tau\varepsilon\vartheta\acute{\varepsilon}\nu\tau o \varsigma~
\pi\lambda\acute{\eta}\vartheta\ o \upsilon\varsigma~
\pi\varrho\acute{\omega}\tau\omega\nu~
\grave{\alpha}\varrho\iota\vartheta\mu\tilde{\omega}\nu,
$$
the English translation of which is: the prime numbers are more than 
any previously existing amount of prime numbers.
}]\label{thm-pz-euklid} % Ende der Fuﬂnote
% Fussnote VOR "]" in [Euclid], damit kein Leerraum vor der Fussnotennummer.
% Vorher stand da: ...(Euclid). BLANK Fussnote und das Blank stoerte.
% Nun steht die Fussnote direkt hinter "Euclid" und vor der ")".
% Eigentlich h‰tte ich sie gerne direkt hinter "(Euclid)", noch vor dem 
% automatisch gesetzten Punkt. 
The sequence of prime numbers does not discontinue.
Therefore, the quantity of prime numbers is infinite.
\end{theorem}
His proof that there is an infinite number of
primes is still considered to be a brilliant mathematical consideration and
conclusion today (\textbf{proof by contradiction} \index{Proof by contradiction}). 
He assumed that there is only a finite number of primes and therefore a 
largest prime number. Based on this assumption, he drew logical conclusions
until he obtained an obvious contradiction. This meant that something must
be wrong. As there were no mistakes in the chain of conclusions, it could
only be the assumption that was wrong. Therefore, there must be an infinite
number of primes!\\

\hypertarget{euclid}{}
\index{Euclid's proof by contradiction}\index{Proof by contradiction}
% \paragraph*{Euclid's proof by contradiction}
% goes as follows:
\begin{Proof}{according to Euclid (proof by contradiction)\\}
{\bf Assumption:} \quad There is a {\em finite} number of primes. \\*[4pt] {\bf
Conclusion:} \quad Then these can be listed $p_1 < p_2 < p_3 < \dots < p_n$,
where $n$ is the (finite) number of prime numbers. $p_n$ is therefore the
largest prime. Euclid now looks at the number $a = p_1 \cdot p_2 \cdots p_n +1$.
This number cannot be a prime number because it is not included in our list of
primes. It must therefore be divisible by a prime, i.e. there is a natural
number $i$ between $1$ and $n$, such that $p_i$ divides the number $a$. Of
course, $p_i$ also divides the product $a-1 = p_1 \cdot p_2 \cdots p_n$, because
$p_i$ is a factor of $a-1$. Since $ p_i $ divides the numbers $ a $ and $ a-1 $,
it also divides the difference of these numbers. Thus: $p_i$ divides  $a - (a-1)
= 1$. $p_i$ must therefore divide $1$, which is impossible. \\*[4pt] {\bf
Contradiction:} \quad Our assumption was false.

@@

Mersenne claimed that $2^{67}-1$ is a prime number. There is also a mathematical
history behind this claim: it first took over 200 years before 
\index{Lucas, Edouard} Edouard Lucas (1842-1891) proved that this number 
is composite.
However, he argued indirectly and did not name any of the factors. In 1903,
Cole\index{Cole, Frank Nelson}\footnote{%
Frank Nelson Cole, American mathematician, Sep. 20, 1861 $-$ May 26, 1926.}
showed which factors make up this composite number: 
$$ 2^{67} -1
=147, 573, 952, 589, 676, 412, 927 = 193, 707, 721 \cdot 761, 838, 257, 287. $$
He admitted to having worked 20 years on the factorization 
\index{Factorization} (expression as a product of prime factors)\footnote{%
  Using CT1\index{CrypTool 1} you can factorize numbers in the 
  following way: menu {\bf Indiv. Procedures \textbackslash{} RSA Cryptosystem 
  \textbackslash{} Factorization of a Number}. \\
  CT1 can factorize with the quadratic sieve (QS) on a single PC in a reasonable
  time numbers no longer than 250 bit.
  Numbers bigger than 1024 bits are currently not accepted by CT1. \\
  With CT2 you can use both the QS and the GNFS (general number field sieve),
  and CT2 can distribute the calculations on several computers.\\
  The current factorization records are listed in chapter \ref{nt:NoteFactorization}.
  \index{Factorization!factoring records}
}
of this 21-digit decimal number!

@@

% --------------------------------------------------------------------------
% \vskip +10 pt
\newpage
\subsection{Unproven statements / conjectures about primes / further open questions}
\begin{itemize}
  \item Goldbach\footnote{%
     Christian Goldbach\index{Goldbach, Christian}, German mathematician,
     Mar 18, 1690$-$Nov 20, 1764. }
     conjectured: Every even natural number greater than 2 can
     be represented as the sum of two prime numbers.

@@

% --------------------------------------------------------------------------
\vskip +10 pt
\hypertarget{HT-GoldbachConjecture}{}
\subsection{The Goldbach conjecture}
\label{L-GoldbachConjecture}

@@

Similarily easy it can be shown, that the weak Goldbach conjecture implies the above mentioned conjecture from Terence Tao (both hold for odd numbers):
\begin{itemize}	
   \item For odd numbers $u>5$ directly the weak Goldbach conjecture implies
         that the sum consits at most of five primes.
   \item For the remaining odd numbers $3$ and $5$ you can directly check it:\\
         $3 = 3$ (the ``sum'' has only one and therefore at most five prime
         summands);\\
         $5 = 2 + 3$ (the sum has two  and therefore at most five prime
         summands).
\end{itemize}

@@

For larger sequences, it is impractical to print all single messages indicating
the primality of integers. In the following Sage session, only the statistics at
the end is printed (by setting the verbose parameter to false): the overall
number of primes and the percentage of primes, generated by $f(n)$ where
$0 \leq n \leq 1000$.

@@

% --------------------------------------------------------------------------
\newpage
% \section*{Web links} \addcontentsline{toc}{section}{Web links}
\chapter*{Web links} \addcontentsline{toc}{section}{Web links}

@@

\item Showing the $n$-th prime number P(n)\\
      \url{http://www.utm.edu/research/primes/notes/by_year.html}
